---
title: "Comparision between timetk and tidyvert family-Part 2"
description: |
  Showcase and reviewing the different tools and technique within the tidyvert and timetk collection that allow user to be able to perform data wrangling, data decomposition as well as feature extraction for time series analysis
author:
  - name: Ginice Seah
    url: https://www.linkedin.com/in/giniceseah/
date: 07-15-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE, message=FALSE,warning=FALSE,fig.width=10,fig.height =10)
```

# Introduction

As mentioned in my earlier post, in this article we will be continuing our reviewing the current techniques used by *timetk* collection on how the data structure is being set up to perform data cleaning and wrangling after the extraction of dataset via web scrapping. 

After which, we will be reviewing the ability to perform feature engineering to look at how time series features, decompositions, statistical summaries and convenient visualizations could be perform by *timetk* collection.

# Setting up environment

Similarly, we would first start with setting up the environment and installation of the packages required for data transformation using R. To ensure that we had cleared the environment to perform data manipulation, we would remove prior R object using the code below

```{r}
rm(list=ls())
```

Next, we would run the following code chunk to validate if the required packages are installed. In the event that the packages are not installed, the code will install the missing packages. Afterwhich, the code would read the required package library onto the current environment.

```{r}
packages = c('tidyverse','tidyquant','tsibble','timetk','feasts','ggplot2','stats','lubridate'
             ,'data.table','rmarkdown','knitr','nycflights13')
for (p in packages) {
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

# Import dataset

In this article, we will be using the same weather dataset from the *nycflights13* package would be used and re-ingested to ensure that the comparison of the *tidyvert* and *timetk* collection is consistent.

The dataset is inclusive of 5 set of data points, namely airlines, airports, flights, planes and weather. Over here in this article, we will be using the weather dataset, where it contain weather related variable like temperature, humid and precipitation.

```{r}
weather = read_csv("data/weather.csv")

paged_table(weather)
```

# timetk

The *timetk* collection is a tidyverse toolkit to visualize, wrangle and transform time series data with much more interactive graphical visual. As mention in the post earlier here, we are able to understand and review the different function and tool that is within the *timetk* collection mianly for data visulization.

In this article I will looking into how data manipulation, time series decomposition and feature extraction could be done using *timetk* collection and how it is different from the *tidyvert* collection.

### Data Wrangling

To begin our analysis, similarly as before we will start with data wrangling. We also be injecting the dataset to ensure that the dataset used had not been manipulated using the (\tidyvert* collection. The *timetk* collection includes several essential data wrangling tools. In this article, we will be looking at the following functions:

1. Summarise by Time - Time-based aggregations 

2. Filter by Time - Time-based filtering

3. Pad by Time - Filling in gaps 

#### Summarize by Time

With *summarise_by_time()* we are able to aggregate the dataset with the required period using *SUM()* as well as period smoothing with either *AVERAGE(), FIRST(),LAST()* function. With the *SUM()* function we are able to compute the total humidity level of each week, as shown in the next line of code.

```{r}
weather = weather %>% 
  select(origin, year, month, day, time_hour, temp, humid, precip)

weather %>%
  group_by(origin) %>%
  summarise_by_time(
    time_hour, .by = "week",
    humid = SUM(humid)
  ) %>%
  plot_time_series(time_hour, humid, .facet_ncol = 2, .interactive = FALSE, .y_intercept = 0)
```

Period smoothing can also be computed where using *AVERAGE()* where we will be able to get the dataset average value that help in the smoothing of the weather dataset as shown. Similar technique could be done using *FIRST()* or *MEDIAN()*.

```{r}
weather %>%
  group_by(origin) %>%
  summarise_by_time(
    time_hour, .by = "month",
    adjusted = AVERAGE(humid)
  ) %>%
  plot_time_series(time_hour, adjusted, .facet_ncol = 2, .interactive = FALSE, .y_intercept = 0)
```

#### Filter by Time

In next part of data wrangling, we will looking at time filter to allow user to be able to select the dataset with their required time period using the *filter_by_time()* function. For the weather dataset, we would like to understand how the humidity level had change in the lower half of year 2013, by allocating the start_date to beginning of June and end_date to be the end of December we would be able to filter the required time period.

```{r}
weather %>%
  group_by(origin) %>%
  filter_by_time(time_hour, "2013-06-01","2013-12-31") %>%
  plot_time_series(time_hour, humid, .facet_ncol = 2, .interactive = FALSE, .y_intercept = 0)
```

#### Padding Data

Padding data would implies that we are able to fill in missing datapoint of the dataset which *tidyvert* collection had a similar concept as well. Using the *padr* package within the *timetk* collection, we are able to fill in missing datapoint easily.

Dataset that had been collected at times might not always be completed hence through *pad_by_time()* user will be able to fill in missing data to allow the irregular time series be regular. This is process is done through using *pad_value* where it would auto filling in the missing value/gaps of the weather dataset based on current dataset.

```{r}
full_weather = weather %>%
  pad_by_time(time_hour, .by = "auto") 

head(full_weather)
```

### Time series graphical visuliation

#### Single Plot

After data wrangling of the dataset, we will be looking into the various graphical feature on the ploting of time plot of the weather dataset. Where within the *timetk* collection, the *plot_time_series()* function is used to generates an interactive plotly chart by default.

Also, we are able to use the following two function to allow the time series plot to be much more interactive where setting *.interactive = TRUE* and *.plotly_slider = TRUE* allow the user to hover datapoint and use the date slider at the bottom of the chart.C

ompared to plot using *tidyvert* collection in *feasts* package, the figure plotted using *timetk* allow the user to better understand the dataset and filter the dataset according to their time series analysis needs.

```{r}
full_weather %>%
  plot_time_series(.date_var=  time_hour, .value = humid, 
                   .line_size = 0.2, .line_color = "#3879A3",
                   .title = "Humidity level of hourly meterological data",
                   .x_lab = "Time period",
                   .y_lab = "Humidity Level",
                   .interactive=TRUE, .plotly_slider = TRUE)
```

#### Group Plot

The next line of code would demonstrate how we are able grouped data base on their different origin of the weather dataset with *group_by()* before we plot using *plot_time_series()*. As the dataset consist of humidity level of different origin the time plot above could be rather confusing and does not allow user to be able to understand with its huge volatility. Having a group plot of the individual time plot of each airport, would enable user to have a better judgement.

Other than grouping we are also able to filter dataset to the time period of Q1 only using a combination of *mutate()* and *filter()*. Moreover, we are also able to apply different color to each of the week number using *color_var* within the *plot_time_series()* function. With the *color_var* the date column is transformed into lubridate::month() number.

```{r}
full_weather %>%
  group_by(origin) %>%
  mutate(quarter= case_when(
      month >= 1 & month <= 3 ~ 'Q1'
      , month >= 4 & month <= 6 ~ 'Q2'
      , month >= 7 & month <= 9 ~ 'Q3'
      , month >= 10 & month <= 12 ~ 'Q4')) %>%
  filter(quarter == "Q1") %>%
  
  plot_time_series(.date_var=  time_hour, .value = humid, 
                   .color_var = month(time_hour),      
                   #.facet_ncol = 2, .facet_scales = "free_x",
                   .title = "Humidity level of hourly meterological data bases on individual origin",
                   .interactive=TRUE)
```

From the above figure, we are able to notice that with the use of *color_var* we better able to identify a common trend of humidity level within the same time period of the three airport location. This further shows the important of color visualization to allow the analysis to be more effective.

Also the *timetk* collection allow the time series visualization to be converted from interactive *plotly* to static format of *ggplot2* just by changing the interactive option from *TRUE* to *FALSE* as shown in the code below. From this user, is easily able to translate their result onto their report or presentation while having the ability to choose to have it interactive if required.

```{r}
full_weather %>%
  group_by(origin) %>%
  mutate(quarter= case_when(
      month >= 1 & month <= 3 ~ 'Q1'
      , month >= 4 & month <= 6 ~ 'Q2'
      , month >= 7 & month <= 9 ~ 'Q3'
      , month >= 10 & month <= 12 ~ 'Q4')) %>%
  filter(quarter == "Q1" & origin == "JFK") %>%
  
  plot_time_series(.date_var=  time_hour, .value = humid, 
                   .color_var = month (time_hour), 
                   .interactive=FALSE,
                   .facet_ncol = 2, .facet_scales = "free",
                   .title = "Humidity level of hourly meterological data bases on individual origin",
                   .x_lab = "Time period",
                   .y_lab = "Humidity Level",
                   .color_lab = "Month") + scale_y_continuous(labels = scales::comma_format())
```

### Correlation Plot in time series

As mentioned before, correlation analysis is done in time series where we will be using autocorrelation to measure the linear relationship between lagged values of a time series. As some of the past lags have predictive information that would be useful in our forecast of the predicted time series. 

Measuring level of correlation between a series and its lags using the *timetk* package is performed using *plot_acf_diagnostics()*, where we are able to compute ACF and PACF with the desired lag time that user input.

* ACF plot - Autocorrelation between a target variable and lagged versions of itself

* PACF plot - Partial Autocorrelation removes the dependence of lags on other lags highlighting key seasonalities.

```{r}
weather %>%
    group_by(origin) %>%
    plot_acf_diagnostics(
        time_hour, humid,               # ACF & PACF
        .lags = "9 days",          # 9-Days of hourly lags
        .interactive = TRUE
    )
```

The formula for the critical value is +1.96/sqrt(n) and -1.96/sqrt(n) where n is the length of the time series. This is to ensure the significance of the ACF plots and that for a white noise time series, 95% of the acf points should fall within this range. 

As the figure plotted above is not the usual ACF plot, it is rather difficult to translate the ACF result to under at which lag k would the time series cut. We will be reploting the ACF value with the used of the *full_weather_acf* dataset that we had compuated using the *tidyverse* collection. After we had calculated the ACF value of each lag k and its critical value, we will then use *ggplot2* package to plot out the common ACF plot for interpretation.

```{r}
weather_tsbl = as_tsibble(full_weather, key = origin, index = time_hour)
weather_tsbl = weather_tsbl %>%
  fill_gaps() %>% 
  group_by_key() %>% 
  tidyr::fill(temp, humid, .direction = "down")

full_weather_2013 = weather_tsbl %>%
  filter(origin == "JFK") %>%
  mutate(quarter= case_when(
      month >= 1 & month <= 3 ~ 'Q1'
      , month >= 4 & month <= 6 ~ 'Q2'
      , month >= 7 & month <= 9 ~ 'Q3'
      , month >= 10 & month <= 12 ~ 'Q4')) %>%
    select(origin, month, temp, humid, precip) 

full_weather_acf=full_weather_2013 %>% ACF(humid, lag_max = 36)

full_weather_acf_plot = full_weather_acf %>%
  mutate(Upper_critical=1.96/sqrt(8730)) %>%
  mutate(Lower_critical=-1.96/sqrt(8730))

head(full_weather_acf_plot)
```

Similar result as the *tidyvert* package is observed where the ACF plot shows that the dataset is not stationary and that it contain a seasonal pattern. The following code chunk, would display the how the ACF plot would be manually plot with the use of having line and bar plot in one figure.

```{r}
ggplot()+
  geom_bar(data=full_weather_acf_plot, aes(x = lag ,y = acf), 
           stat='identity',width = 0.01, color = "black") +
  geom_line(data=full_weather_acf_plot, aes(x = lag ,y = Upper_critical), 
           stat='identity',width = 0.05, color = "blue",linetype = 2) +
  geom_line(data=full_weather_acf_plot, aes(x = lag ,y = Lower_critical), 
           stat='identity',width = 0.05, color = "blue",linetype = 2) +
  labs(title = 'ACF plot of humidity level at JFK '
       ,y = 'ACF value'
       ,x = 'Lag') +
  theme(text = element_text(color = "#444444", family = 'Helvetica Neue')
        ,plot.title = element_text(size = 26, color = '#333333')
        ,plot.subtitle = element_text(size = 13)
        ,axis.title = element_text(size = 14, color = '#333333')
        ,axis.title.y = element_text(angle = 0, vjust = .5)
        )
```

### Seasonality plot in time series

Beside the single and group time series visualization, *timetk* collection allow user to perform visualize the time series by seasonality (in hours, days, weeks or months).By using the *plot_seasonal_diagnostics()* function as shown in the code below, we are able to identify any seasonal trend or hidden pattern of the whole weather dataset or individual airport weather dataset as shown in the plot below respectively.

```{r}
weather %>%
    plot_seasonal_diagnostics(time_hour, humid, .interactive = FALSE)
```

```{r}
weather %>%
  group_by(origin) %>%
    plot_seasonal_diagnostics(time_hour, humid, .interactive = FALSE)
```

### Anomaly detection

Another important function of *timetk* would be the easiness to perform anomaly detection. Anomaly detection is where we identify data point that has unusual high/low value within the dataset. In other words, that data point is different from the rest.

In *timetk*, we are able to identify anomaly detection visualization using *plot_anomaly_diagnostics()* function and to split the dataset by year. The code below allow us to be to identify the anomaly detection for the humidity level of the weather dataset in year 2013. Hence, we can see from the figure below that the dataset do not contain anomalies datapoint as it did not flag out any red dots.

```{r}
weather %>%
  group_by(origin) %>%
  filter(origin == "JFK") %>%
  plot_anomaly_diagnostics(time_hour, humid, .interactive=TRUE)
```

Overall, with *timetk* we are able to perform time series analysis with a greater control in data visulization. This is especially so with the different interactive function that allow data filtering, data selection and colourization of the graphical visual to be much simpler. With those build-in function within the *timetk* collection, user is able to be focus in the building of report apporved time series graphical visulization.

Also, even though the data wrangling tool that *timetk* collection had is very similar to those in *tidyvert* collection. The advantage of the *timetk* is the ability to work in both traditional R dataframe as well as tsibble dataframe. This is especially useful for raw dataset that is rather messy and unstructured, to get a quick analysis we are able to select the required variable and perform a quick time series analysis with *timetk*

However, the one of the limitation of the *timetk* collection is the different from norm approach of ploting ACF plot using the function within *timetk* collection. This non-standardize approach might add confusion to user that are familar with the usual ACF plot as shown in the *tidyvert* collection. 

# Conclusion

Overall, both *tidyvert* and *timetk* collection had enhanced the whole time series analysis experience since the *forcast* package days. From a very statics approach in the past to a much more interactive graphical visual. This whole new experience, allow the user to have more control and ability to beautify their various time series plots and ehanced the whole coding experience with various build-in function.

As mentioned earlier, *tidyvert* collection is a much more suitable approach for a standardize tsibble dataframe format while *timetk* collection is useful for a quick analysis of any dataframe format. 

In terms of time series visualization, *timetk* collection is much more interactive as it allow dataset to be filtered for selected time period with slider, ability to look into details by hovering data as well as the ability to color datapoint by time period which is a function that was really useful through my review.

# Reference

* 8.2 Cross Correlation Functions and Lagged Regressions: STAT 510. PennState: Statistics Online Courses. (n.d.). https://online.stat.psu.edu/stat510/lesson/8/8.2. 
* Automatic Anomaly Detection. • timetk. (n.d.). https://business-science.github.io/timetk/articles/TK08_Automatic_Anomaly_Detection.html. 
* Baranovskiy, P. (2021, January 1). Correlation Analysis in R, Part 1: Basic Theory: R-bloggers. R. https://www.r-bloggers.com/2021/01/correlation-analysis-in-r-part-1-basic-theory/. 
Blog, P. by 						D. C. (2017, March 21). R Correlation Tutorial: R-bloggers. R. https://www.r-bloggers.com/2017/03/r-correlation-tutorial/#:~:text=A%20correlation%20coefficient%20of%20%2D1,x. 
* chirag676. (2021, April 26). Correlation: Intuition Behind Correlation - Definition and It's Types. Analytics Vidhya. https://www.analyticsvidhya.com/blog/2021/04/intuition-behind-correlation-definition-and-its-types/. 
* Create a rolling version of any function - rollify. - rollify • tibbletime. (n.d.). https://business-science.github.io/tibbletime/reference/rollify.html. 
* E. E. Holmes, M. D. S. (2021, March 1). Applied Time Series Analysis for Fisheries and Environmental Sciences. 4.4 Correlation within and among time series. https://nwfsc-timeseries.github.io/atsa-labs/sec-tslab-correlation-within-and-among-time-series.html. 
* Evaluation, S. (n.d.). R Software Handbook. 6 Data Visualization with ggplot. https://bookdown.org/aschmi11/RESMHandbook/data-visualization-with-ggplot.html. 
* Forecasting: Principles&nbsp;and&nbsp;Practice (3rd ed). 2.1 tsibble objects. (n.d.). https://otexts.com/fpp3/tsibbles.html. 
* Forecasting: Principles&nbsp;and&nbsp;Practice (3rd ed). 2.4 Seasonal plots. (n.d.). https://otexts.com/fpp3/seasonal-plots.html. 
* Forecasting: Principles&nbsp;and&nbsp;Practice (3rd ed). 2.7 Lag plots. (n.d.). https://otexts.com/fpp3/lag-plots.html. 
* Forecasting: Principles&nbsp;and&nbsp;Practice (3rd ed). 2.8 Autocorrelation. (n.d.). https://otexts.com/fpp3/acf.html. 
* Forecasting: Principles&nbsp;and&nbsp;Practice (3rd ed). Chapter 3 Time series decomposition. (n.d.). https://otexts.com/fpp3/decomposition.html. 
* Hadley Wickham [aut, cre]. (2021, April 12). flights: Flights data in nycflights13: Flights that Departed NYC in 2013. https://rdrr.io/cran/nycflights13/man/flights.html. 
* Hyndman, R. on R. J. (2019, August 29). Tidy time series data using tsibbles: R-bloggers. R. https://www.r-bloggers.com/2019/08/tidy-time-series-data-using-tsibbles/. 
* Hyndman, R. on R. J. (2019, August 30). Time series graphics using feasts: R-bloggers. R. https://www.r-bloggers.com/2019/08/time-series-graphics-using-feasts/. 
* Khalid, I. A. (2021, May 19). Timetk: The R Library for Time Series Analysis. Medium. https://towardsdatascience.com/timetk-the-r-library-for-time-series-analysis-9822f7720318. 
* Masaaki Horikoshi [aut], Y. T. [aut. (2021, July 8). autoplot.forecast: Autoplot 'forecast::forecast' in ggfortify: Data Visualization Tools for Statistical Analysis Results. https://rdrr.io/cran/ggfortify/man/autoplot.forecast.html. 
* Missing Value Imputation for Time Series - ts_impute_vec. - ts_impute_vec • timetk. (n.d.). https://business-science.github.io/timetk/reference/ts_impute_vec.html. 
* Mitchell O'Hara-Wild [aut, cre]. (2021, June 3). gg_tsdisplay: Ensemble of time series displays in feasts: Feature Extraction and Statistics for Time Series. https://rdrr.io/cran/feasts/man/gg_tsdisplay.html. 
* Mutate multiple columns - mutate_all. - mutate_all • dplyr. (n.d.). https://dplyr.tidyverse.org/reference/mutate_all.html. 
* O'Hara-Wild, M. (2020, November 18). Introducing feasts. https://www.mitchelloharawild.com/blog/feasts/. 
* Plotting Seasonality and Correlation. • timetk. (n.d.). https://business-science.github.io/timetk/articles/TK05_Plotting_Seasonality_and_Correlation.html. 
* plot_acf_diagnostics: Visualize the ACF, PACF, and CCFs for One or More Time Series. RDocumentation. (n.d.). https://www.rdocumentation.org/packages/timetk/versions/2.6.1/topics/plot_acf_diagnostics. 
* plot_time_series: Interactive Plotting for One or More Time Series. RDocumentation. (n.d.). https://www.rdocumentation.org/packages/timetk/versions/2.6.1/topics/plot_time_series. 
* Science, B. (2020, August 26). Time Series in 5-Minutes, Part 4: Seasonality: R-bloggers. R. https://www.r-bloggers.com/2020/08/time-series-in-5-minutes-part-4-seasonality/. 
* Tidy Temporal Data Frames and Tools. Tidy Temporal Data Frames and Tools •. (n.d.). https://tsibble.tidyverts.org/. 
* Tidy time series data using tsibbles. Portrait of the author. (2019, August 29). https://robjhyndman.com/hyndsight/tsibbles/. 
* tidyverts. (n.d.). https://tidyverts.org/. 
* Time Series Data Wrangling. • timetk. (n.d.). https://business-science.github.io/timetk/articles/TK07_Time_Series_Data_Wrangling.html. 
* Time series graphics using feasts. Portrait of the author. (2019, August 30). https://robjhyndman.com/hyndsight/feasts/. 
* A Tool Kit for Working with Time Series in R. A Tool Kit for Working with Time Series in R •. (n.d.). https://business-science.github.io/timetk/. 
* Vaughan, D. (2020, July 21). Rolling calculations in tibbletime. https://cran.rstudio.com/web/packages/tibbletime/vignettes/TT-03-rollify-for-rolling-analysis.html. 
* Visualizing Time Series. • timetk. (n.d.). https://business-science.github.io/timetk/articles/TK04_Plotting_Time_Series.html. 
* Visualizing Time Series. • timetk. (n.d.). https://business-science.github.io/timetk/articles/TK04_Plotting_Time_Series.html. 
* Wang, E. (n.d.). Introduction to tsibble. https://cran.rstudio.com/web/packages/tsibble/vignettes/intro-tsibble.html. 
* Wickham, H. (2021, April 12). Flights that Departed NYC in 2013 [R package nycflights13 version 1.0.2]. The Comprehensive R Archive Network. https://cran.r-project.org/web/packages/nycflights13/index.html. 
